--- 
title: "Text Mining for Technical Knowledge Extraction"
author: "Filippo Chiarello"
date: "`r Sys.Date()`"
bibliography:
- book.bib
- packages.bib
description: Test uno, due, tre, quattro description.
documentclass: book
link-citations: yes
site: bookdown::bookdown_site
biblio-style: apalike
---

# Prerequisites


<!--chapter:end:index.Rmd-->

# Introduction {#intro}

You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].

<!--chapter:end:01-introduction.Rmd-->

# State of the Art

Here is a review of existing methods.

## Tools 

## Documents

### Patents

### Papers

### Projects

### Wikipedia

### Twitter

### Job Profiles

<!--chapter:end:02-state_of_the_art.Rmd-->

# Methods

We describe our methods in this chapter.

## Patents

## Papers

## Projects

## Wikipedia

## Twitter

## Job Profiles

<!--chapter:end:03-methods.Rmd-->

# Applications

Some _significant_ applications are demonstrated in this chapter.

## Patents

## Papers

## Projects

## Wikipedia

## Twitter

## Job Profiles

<!--chapter:end:04-case_studies.Rmd-->

# Future Developments

Decide the way in wich devide the chapter. Tools or functions?

## Research and Development

## Marketing

## Human Resources

<!--chapter:end:05-future_developments.Rmd-->

# Final Words

We have finished a nice book.

<!--chapter:end:06-conlusion.Rmd-->

`r if (knitr::is_html_output()) '
# References {-}
'`

<!--chapter:end:07-references.Rmd-->

